---
output:
  word_document: default
---
---
Title: "final_report"
Author: "GROUP 6"
Date: "1/7/2021"
output: word_document
INTRODUCTION
Our research is to find the correlation between points gained and time of play at the 2019-2020 season of the NBA. The data set for this research was gotten via the -URL:https://www.kaggle.com/calvingee/nba-stat-projections-2019 
The data set attributes different features(columns)to 287 respective players at the NBA for the season.

RQ: Is there a correlation between the time played in (minutes) and the number of points gained at the 2019-2020 season of the NBA?
-
-Null hypothesis: There is no correlation between the time played in (minutes) and the number of points gained at the 2019-2020 season of the NBA.
-
-Alternative hypothesis:  There is a correlation between time played in (minutes) and the number of points gained at the 2019-2020 season of the NBA.
```{r Message=FALSE, echo=FALSE}
library(readr)
FantasyPros_Fantasy_Basketball_Overall_2019_Projections <- read_csv("FantasyPros_Fantasy_Basketball_Overall_2019_Projections.csv")
summary(FantasyPros_Fantasy_Basketball_Overall_2019_Projections)
```
VISUALIZATION
The scatter plot shows a positive correlation between our two variables.This implies that the number of points gained by a player increases with the time of play.

The histogram is skewed to the right, which implies that our data is not normally distributed.The mean, given in the output below is higher than the mode and median.

```{r Message=FALSE, echo=FALSE}
x <-FantasyPros_Fantasy_Basketball_Overall_2019_Projections$MIN
y <-FantasyPros_Fantasy_Basketball_Overall_2019_Projections$PTS
plot(x, y, las=1, xlab = "Time played (minutes)" , ylab = "Number of points gained" , main = "Timed played in minutes vs Number of points gained\nat the 2019-2020 season of the NBA" , pch =20 , frame =T)
model <- lm(y ~ x,data =FantasyPros_Fantasy_Basketball_Overall_2019_Projections)
abline(model,col ="red")
histogram <-hist(y,10, main = "Distribution of number of points gained\nat the 2019-2020 season of the NBA",xlab = "Number of points" ,ylab = "frequency", col="blue")
x1 <- seq(0, 2600, 1)
mn <- mean(y)
print(mn)
y1 <-dnorm(x1,mean = mn,sd=sd(y))
box.size<-diff(histogram$mids[1:2]) *length(y)
y1<-y1 *box.size
lines(x1, y1, col="red")
dev.off()
```
ANALYSIS
Using Kendall's tau,to test the correlation of our non-parametric data, the  positive correlation coefficient of 0.73. We have a strong linear relationship between the number of points gained and the time of play.
The P value,p-value < 2.2e-16 is much smaller than the significance value of 0.05. This implies that there is a significant relationship between the number of points gained and the time of play. 


```{r Message=FALSE, echo=FALSE}
cor(x,y,use ="pairwise.complete.obs",method = "kendall")
cor.test(x,y,method ="kendall")
```
CONCLUSION
Using Kendall's tau, there is a significant correlation between the time played in (minutes) and the number of points gained at the 2019-2020 season of the NBA.
Hence,the Null hypothesis can be rejected.

